Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-23 ms.tex
maturation trait
some runs

    \item search speed, the distance that a searching male will cover in one time step, see Fig. \ref{fig:area searched}.
    Trade offs:
        \begin{itemize}
            \item higher metabolic cost of search
            \item higher predation rate
        \end{itemize}
\end{enumerate}

@@

$c_n$ is called the stochastic reaction constant\\
$c_n \cdot dt = $ the average probability that a particular combination of $R_n$, reactant molecules will react accordingly in the next infinitesimal time interval $dt$\\

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched my a male in interval $dt$}
\label{fig:area searched}
\end{figure}
\clearpage

>>>>

    \item search speed, the distance that a searching male will cover in one time step, see Fig. \ref{fig:area searched}.
    Trade offs:
        \begin{itemize}
            \item higher metabolic cost of search
            \item higher predation rate
        \end{itemize}
    \item maturation time, the time at which to mature is inherited as well but with a constant level of noise
\end{enumerate}

@@

$c_n$ is called the stochastic reaction constant\\
$c_n \cdot dt = $ the average probability that a particular combination of $R_n$, reactant molecules will react accordingly in the next infinitesimal time interval $dt$\\
s
\begin{verbatim}
I have the probability of encountering a   
\end{verbatim}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched by a male in interval $dt$}
\label{fig:area searched}
\end{figure}
\clearpage
